The effect of detector nonlinearity on \wfa\ PSF profiles for weak gravitational lensing measurements

### 2016-01-23 bias_from_NL.tex
changes by chaz, roger, jason, before sending to group

%\title{Voltage non-linearity effects on \wfa\ PSF profiles for weak lensing measurements using {\tt{GalSim}} simulations}
\title{The effect of detector nonlinearity on \wfa\ PSF profiles for weak gravitational lensing measurements}
\author{A. A. Plazas$^{\dagger a}$, C. Shapiro$^{a,b}$, J. Rhodes$^{a,b,c}$, \& R. Smith$^b$}
\email{$^\dagger$andres.a.plazas.malagon@jpl.nasa.gov}
\affil{$^a$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Dr., Pasadena, CA 91109, USA}
\affil{$^b$California Institute of Technology, 1200 E. California Blvd, CA 91125, USA}
\affil{$^c$Institute for the Physics and Mathematics of the Universe, 5-1-5 Kashiwanoha, Kashiwa, Chiba Prefecture 277-8583, Japan }
\begin{abstract}
Weak gravitational lensing (WL) is one of the most powerful techniques to learn about the dark sector of the universe. To extract the WL signal from astronomical observations, observed galaxy shapes must be measured and corrected for the Point Spread Function (PSF) of the imaging system with extreme accuracy (of the order of 1 part per 1000 in the fractional and absolute errors in size and ellipticity). Biases in shape measurements can potentially originate in the detectors by any particular instrument. Future missions such as NASA's Wide Field Infrared Survey Telescope-Astrophysics Focused Telescope Asset (\wfa) will use a new family of hybrid near-infrared CMOS detectors (HAWAII-4RG) that are untested for accurate WL measurements. Like any other detector, these devices are intrinsically subject to non-linearities in the conversion of photo-generated charge to measured voltage that tend to attenuate bright objects such as reference stars that are used for PSF determination. In this paper, we study and set preliminary requirements on the impact on \wf\ PSF properties (size and ellipticity) induced by this type of detector non-linearity (NL), setting preliminary requirements We use the publicly-available \gs\ and the \wf\ Exposure Time Calculator codes to generate customized simulations of the PSF optical profiles expected for \wf\ and study the consequences of a one-parameter non-linearity function quadratic in the signal $Q$ (in electrons) per pixel, $f(Q)=Q-\beta Q^2$. We use these simulations to measure the fractional error in the PSF size ($\Delta R/R$) and the absolute error in the PSF ellipticity ($\Delta e$) as a function of parameters such as the expected magnitude of typical stars in \wf\ and  $\beta$. For a nominal $\beta_0=3.566\times10^{-7}/e^{-}$, NL attenuates the signal by $\sim 4\%$ for a pixel full well depth of about $1.1^5$ e$^-$. Since the NL effects depend on PSF size and flux, we find variation in its amplitude among the four bands of the High Latitude Survey (HLS) of \wf\ (being the largest for the J129 band). As $\beta$ is allowed to increase, the values of $\Delta R/R$ and $\Delta e$ increase linearly in all bands at a fixed magnitude. Uncalibrated, NL at its nominal value can induce an error of $\Delta R/R=2.5\times 10^{-3}$ and $\Delta e_2=5\times^{-4}$ in the \wf\ PSF size and ellipticity in the H158 bandpass for the expected brightest stars (AB magnitude of $\sim m=20$) in the HLS of \wf. In addition, our simulations show that to limit the bias of $\Delta R/R$ and $\Delta e$ in the H158 band to better than 1 part in 1000, the mean $\beta$ must be calibrated to $\sim3.5\%$ and $\sim 10\%$, respectively. 
\end{abstract}

@@

Systematic errors that originate from a telescope's detectors (image sensors) can introduce biases in astronomical observables such as photometry and astrometry that propagate into shear measurement biases. These type of errors have been extensively studied in the case of thick, fully-depleted, high-resistivity Charge Coupled-Devices (CCDs), which are the detectors of choice for many current and planned surveys such as DES, HSC, and LSST \citep{stubbs14,plazas14,gruen15}. It is of great importance to qualitatively quantify the impact of these sensor effects on the inference of cosmological parameter, in particular through WL \citep{jarvis14,mandelbaum14b,meyers14}. Future missions such as the James Webb Space Telescope and \wfa\ will utilize a new family of near-infrared detectors that are subject as well to effects such as non-linearity, reciprocity failure \citep{bohlin05,biesiadzinski11}, interpixel capacitance (IPC) \citep{mccullough08,kannawadi15}, and persistence \citep{smith08}, and that can potentially imprint biases on weak lensing shape measurements if not taken into account.

@@

In Section \S2 we summarize the main characteristics of the NIR detectors that will be used in \wfa\, and describe NL. In Section \S3 we describe the simulations we create to study NL for \wfa\ PSF profiles. Section \S4 presents our main results on fractional errors in size and absolute errors in ellipticity caused by NL, as function of relevant parameters such as mean non-linearity amplitude and PSF magnitude. We conclude in Section \S5 with a discussion of our results and how they can be used in the derivation of NIR detector specifications to satisfy WL accuracy requirements.

@@

The last two types of non-linearity depend on fluence (total flux per pixel, or integrated signal, as opposed to RF, which is flux dependent), and can be analyzed together in a singe transfer function typically called ``nonlinearity". We study the impacts of NL (more relevant at high signals) on PSF measurements in this paper, while we leave investigations on the consequences of RF (relevant at lower signals) on WL measurements for future work.

Measurements with H2RG 1.7$\mu$m cutoff detectors produced for the NIR channel of the Wide Field Camera 3 (WFC3) installed onboard the Hubble Space Telescope (with the same basic design of the H4RG that will be used in the WFI but with 18 $\mu$m pixels) show that the voltage relation for a measured signal $S$ is well fit by a quadratic function in the \emph{mean} signal $\langle Q \rangle$ of the form:
\begin{align}
S(\langle Q \rangle)=\langle Q \rangle-\beta \langle Q \rangle^2 \ \ (e^{-})
\label{NL}
\end{align}
We \emph{assume} that each individual pixel satisfies a NL function of the same form as Eq. \ref{NL}, and that the spatial variation on NL is such as the non-linearity coefficient $\beta$ in each pixel can be drawn from a Normal distribution of the form $\mathcal{N} \sim (\beta_0, 0.12\beta_0)$, where the nominal value $\beta_0 \equiv 3.566\times10^{-7}/e^{-}$ and the dispersion parameter of the distribution (r.m.s.$=0.12\beta_0$) includes shot noise and deviations of the individual NL curves from the mean NL. This mean nominal value implies an attenuation of the signal of about $4\%$ for a pixel full well depth in the WFI detectors of $1.1 \times 10^5$ electrons \footnote{Dave Content (GSFC), private communication.} (Eq. \ref{NL}). We assume that galaxies will have about two orders of magnitude less total electrons than bright stars, and therefore for this quadratic model, star shapes are distorted by NL and galaxies are (approximately) not, which would result in incorrect PSF correction if not accurately calibrated. We have verified that the results using the mean NL coefficient for all pixels do not differ significatively from those using the distribution above for each pixel.

We apply this mapping to simulated \wfa\ PSF profiles and quantify the impact on PSF properties such as size and shape.

@@

\citet{kannawadi15} have developed within \gs\ (v1.3) a \wfa\ module called ``{\tt{galsim.wfirst}}", which allows the simulation of a PSF profile according to the optical design characteristics of the \wfa\ WFI \citep{pasquale14})\footnote{\citet{pasquale14} discuss the so-called ``Cycle 4" optical design, whereas the \gs\ \wfa\ module -used in this work- uses files corresponding to ``Cycle 5"}) through the calling of {\tt{galsim.wfirst.getPSF}} routine. This routine returns a {\tt{python}} dictionary of {\tt{galsim.ChromaticOp-}}\\{\tt{ticalPSF}} objects indexed by each one of the 18 H4RG detectors of the FPA. It uses the optical configuration of the pupil plane to simulate PSF images in any \wfa\ WFI bandpass filter, with expected optical aberrations approximated as a linear combination of Zernike polynomials (up to Noll order equal to $11$, \citet{noll67}). For this work, we have created simulations in four bands of the HLS (see Table 1).  A central circular obscuration ($30 \%$) and six support struts are included as well. The pupil plane configurations and Zernike models are publicly available.\footnote{\url{http://wfirst.gsfc.nasa.gov/science/sdt_public/wps/references/instrument/}}

@@

To overcome this problem in real data, multiple dithered exposures are taken, and then put together by means of an image combination algorithm\citep{lauer99b,fruchter02,bertin06,rowe11} in order to produce an oversampled image that satisfies the Nyquist-Shannon criterium. To study NL with simulations, however, we do not make use of such external software\textemdash which can be computationally expensive\textemdash to produce an image at higher resolution. Instead, we have used an approximation where we draw \gs objects at a high resolution through the method {\tt{galsim.GSObject.drawImage}}\footnote{The keyword {\tt{method}} should be set to {\tt{`no\char`_pixel'}} when calling {\tt{galsim.GSObject.drawImage}}, since by default it convolves its argument profile with a boxcar of length {\tt{pixel\char`_scale}}. This extra convolution must be turned off because the effective PSF profile we create already includes this pixel response.}, setting the parameter {\tt{scale}} to $p/N$, where $N\in \mathbb{Z}^{+}$ and $p$ is the native pixel scale. We apply the effect of NL to the convolved PSF profile, including the pixel response at its native scale, and then render it with a resolution $p/N$. 
Defining $Q\equiv1/p\times u_{\text{max}}$ as the sampling factor ($Q<2$, $Q=2$, and $Q\geq2$ represent under-, critically, and over-sampled images, respectively), we see that in order to produce an over-sampled image ($Q\geq2$), the Nyquist-Shannon criterium implies that $N$ must be given by (see \emph{e.g.}, \citet{marks09,shapiro13})
\begin{align}
N=\frac{2p}{\lambda_{min} F}
\label{nimages}
\end{align}
where $p$ is the pixel size, $\lambda_{min}$ is the shortest wavelength in a given filter, and $F$ is the the f-number of the telescope. In the case of the \wfa\ telescope, $p=10\ \mu$m and $F=7.8$, resulting in $N\geq3$ ($N\geq2$) for the J129 (H158) band. However, we have conservatively chosen a larger $N$ for our simulations to reduce discretization errors. We have verified the convergence of our results for $N\geq6$.  
%However, we oversample the images at  the error due to discretizing, and to reduce the variance due to any sub-pixel offsets that PSFs may have. We have set $N$ equal to $6$ for our simulations.

@@

The PSF profiles are drawn into square postage stamps of size 1.5k pixels (k=1024), large enough to ensure that most of the flux applied to the original profile object is conserved when drawing the image. %In addition, this avoid biases in PSF determination arising from object selection and deblending. 
Each profile object was assigned a total flux of 
\begin{align}
f=k(\lambda)\times2.521^{(20-m)} \ e^{-}, 
\label{flux}
\end{align}
which is the number of source counts per exposure and where $m$ represents the AB magnitude of the object. $k(\lambda)$ e$^{-}$ is a baseline flux at AB magnitude $m=20$ determined by using the \wfa\ Exposure Time Calculator\footnote{\url{https://wfirst.ipac.caltech.edu/sims/tools/wfDepc/wfDepc.html}} \citep{hirata12} in weak lensing mode (ETC-WL). Notice that in our simulations we have neglected the main sources of noise that would affect the HLS (zodiacal background, thermal emission, dark current, and read noise), which would make all images slightly more nonlinear.

@@

The basic process is summarized by the following steps:  
\begin{itemize}
\item[1.] Create a \wfa\ PSF surface brightness profile with a given flux as prescribed by Eq. \ref{flux}. 
\item[2.] Convolve the PSF profile with a squared pixel response with the size of the native plate scale of the \wfa\ FPA ($p=0.11$ arcseconds per pixel) to produce an effective PSF. 
\item[3.] Draw the effective PSF profile in a noiseless postage stamp of size $1.5k$ by $1.5k$ pixels ($k=1024$) pixels at a higher resolution of of $p/N$, with $N=6$, and multiply the resulting image by $N^2$. In this step, NL is not yet applied, but it will be done so in a later step, so the flux still needs to be adjusted. 
\item[4.] Use the adaptive moments algorithm to measure the shape $e=(e_{1,0},e_{2,})$ and size $R_0$ of the profile to have as baseline reference.
\item[5.] Create another image of the effective PSF at a higher resolution and with the flux adjusted as in 3. To apply NL, draw a $\beta$ from the distribution $\mathcal{N} \sim (\beta_0, 0.12\beta_0)$ for each pixel in the high-resolution image $I$, and apply the voltage non-linearity to the postage stamps according to the transformation $I \mapsto I - \beta I^2$ (\emph{c.f.} Eq. \ref{NL}.)
\item[6.] Measure the shape and size of the object with the sensor effect applied, and calculate the quantities $\Delta e_1$, $\Delta e_2$, and $\frac{\Delta R}{R}$, as defined in Eqs. \ref{delta_e} and \ref{delta_r}. 
\item[7.] Repeat steps 5 and 6 for $M$ realizations of the $\beta$ distribution, and calculate the mean value of Eqs. \ref{delta_e} and \ref{delta_r} over all $M$ realizations. The error bars will be given by the standard error of the mean. In our simulations, we use $M=10$. 
\item [8.] Repeat  steps 1 to 7 for different AB magnitudes (fluxes) at fixed mean $\beta$ and for different NL parameters at a fixed magnitude. 
\end{itemize}
\section{Results}
Fig. \ref{beta} shows the fractional change in PSF size and the absolute error in PSF ellipticity as a function of the nonlinearity parameter $\beta$, for different bandpass filters at fixed AB magnitude of 20, consistent with the magnitude of brightest stars that will be usable for the HLS. The effect depends on flux, and hence its amplitude is the largest in the J129 bandpass filter (\emph{c.f.}, Table 1). 
\begin{figure}[!h]
\centering
\resizebox{\hsize}{!}{\includegraphics[page=1]{plots/delta_r_over_r_delta_e_mag20_wfirst_psf_10_realizations_1-18-2016.pdf}}
\caption{Fractional error in PSF size (upper panel) and absolute error in PSF ellipticity components (lower panels) as a function of nonlinearity parameter $\beta$ for the \wfa\ PSF, in four the four HSL filters (J129, Y106, H158, and F184), and an AB magnitude of 20 (similar plots were found for other values of magnitude). In each plot, the nominal value for the nonlinearity parameter as given by laboratory measurements, $\beta_0$, is located at the third point from the origin. Each point is the mean over $M=10$ realizations of the parameter $\beta$ per pixel, and the associated error bars (too small to be seen in the cases of $\Delta R/R$ and $\Delta e_2$) represent the standard error of the mean.}
\label{beta}
\end{figure}
In this band, the nominal value of $\beta_0=3.566\times10^{-7}/e^{-}$ induces errors in the size and ellipticity of about $5\times10^{-3}$ and $8\times10^{-4}$ respectively, comparable or even larger than the required values of $10^{-3}$ and $4.5\times10^{-4}$ on the knowledge of the size and ellipticity of the PSF in order not to bias cosmological parameter inferences from WL experiments (Section \S1). As the $\beta$ parameter is increased, the amplitude of the errors increases approximately in a linear manner within the domain of $\beta$ vales considered.

%It is possible to obtain a more general relationship between $\Delta R/R$ (or $\Delta e$), $\beta$, and object flux for each band by Taylor expanding to first order around any given value in $\beta$ and plotting the slope as a function of magnitude. 
Since $\Delta R/R$ and $\Delta e$ are approximately linear in $\beta$, we can condense this information by simply plotting the slope for various filters and star magnitudes.This is shown in Fig. \ref{magnitude}, which shows $\Delta R/R/\beta$ and $\Delta e/\beta$ (the slopes in Fig. \ref{beta}) vs $m$ for each of the four filters of the HLS. From Fig. \ref{magnitude}, it is possible to estimate the precision to which $\beta$ would have to be calibrated in order to limit the relative size and ellipticity bias of a star with a given magnitude. In particular, letting $(\beta - \beta_0)/\beta_0 \equiv \Delta \beta / \beta_0$ represent the fractional error in the measurement of a given value of $\beta_0$, we have: 
\begin{align}
\frac{\Delta R/R}{\Delta \beta} = c \ \ \ \  \Rightarrow \ \ \ \ \frac{\Delta R/R}{\Delta \beta / \beta_0} = c \beta_0  \ \ \   \Rightarrow \ \ \
\frac{\Delta \beta}{\beta_0} = \frac{\Delta R/R}{c \beta_0}
\label{calib}
\end{align}
In Eq.\ref{calib}, $c$ represents the ordinate value in Fig. \ref{magnitude} for a given magnitude, and we have replaced $\Delta R/R/\beta$ by $\Delta R/R/ \Delta \beta$ since the linearity in the bias in $\Delta R/R$ and $\Delta e$ vs $\beta$ for all magnitudes makes the choice of the expansion point of the Taylor expansion unimportant (\emph{i.e.}, it does not matter if the expansion is around $\beta=0$ or $\beta=\beta_0$). An analogous equation to Eq. \ref{calib} can be written for the error in the ellipticity if $\Delta R/R$ is replaced by $\Delta e$.

@@

>>>>

%\title{Voltage non-linearity effects on \wfa\ PSF profiles for weak lensing measurements using {\tt{GalSim}} simulations}
\title{The effect of detector nonlinearity on \wfa\ PSF profiles for weak gravitational lensing measurements}
\author{A. A. Plazas$^{\dagger a}$, C. Shapiro$^{a,b}$, J. Rhodes$^{a,b,c}$, \& R. Smith$^b$}
\email{$^\dagger$andres.a.plazas.malagon@jpl.nasa.gov}
\affil{$^a$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Dr., Pasadena, CA 91109, USA}
\affil{$^b$California Institute of Technology, 1200 E. California Blvd, CA 91125, USA}
\affil{$^c$Institute for the Physics and Mathematics of the Universe, 5-1-5 Kashiwanoha, Kashiwa, Chiba Prefecture 277-8583, Japan }
\begin{abstract}
Weak gravitational lensing (WL) is one of the most powerful techniques to learn about the dark sector of the universe. To extract the WL signal from astronomical observations, observed galaxy shapes must be measured and corrected for the Point Spread Function (PSF) of the imaging system with extreme accuracy (of the order of 1 part per 1000 in the fractional and absolute errors in size and ellipticity). Biases in shape measurements can potentially originate in the detectors by any particular instrument. Future missions such as NASA's Wide Field Infrared Survey Telescope-Astrophysics Focused Telescope Asset (\wfa) will use a new family of hybrid near-infrared CMOS detectors (HAWAII-4RG) that are untested for accurate WL measurements. Like any other detector, these devices are intrinsically subject to non-linearities in the conversion of photo-generated charge to measured voltage that tend to attenuate bright objects such as reference stars that are used for PSF determination. In this paper, we study and set preliminary requirements on the impact on \wf\ PSF properties (size and ellipticity) induced by this type of detector non-linearity (NL). We use the publicly-available \gs\ and the \wf\ Exposure Time Calculator codes to generate customized simulations of the PSF optical profiles expected for \wf\ and study the consequences of a one-parameter non-linearity function quadratic in the signal $Q$ (in electrons) per pixel, $f(Q)=Q-\beta Q^2$. We use these simulations to measure the fractional error in the PSF size ($\Delta R/R$) and the absolute error in the PSF ellipticity ($\Delta e$) as a function of parameters such as the expected magnitude of typical stars in \wf\ and $\beta$. We study the effect of spatial variation of $\beta$, and find that a mean curve can de used to calibrate for NL. For a nominal mean $\beta_0=3.566\times10^{-7}/e^{-}$, NL attenuates the signal by $\sim 4\%$ for a pixel full well depth of about $1.1^5$ e$^-$. Since the NL effects depend on PSF size and flux, we find variations in its amplitude among the four bands of the High Latitude Survey (HLS) of \wf\ (being the largest for the J129 band). As $\beta$ is allowed to increase, the values of $\Delta R/R$ and $\Delta e$ increase linearly in all bands at a fixed magnitude. Uncalibrated, NL at its nominal value can induce an error of $\Delta R/R=2.5\times 10^{-3}$ and $\Delta e_2=5\times 10^{-4}$ in the PSF size and ellipticity in the H158 bandpass for the expected brightest stars (AB magnitude of $\sim m=20$) in the HLS of \wf. In addition, our simulations show that to limit the bias of $\Delta R/R$ and $\Delta e$ in the H158 band to better than 1 part in 1000, the mean $\beta$ must be calibrated to $\sim3.5\%$ and $\sim 10\%$, respectively. 
\end{abstract}

@@

Systematic errors that originate from a telescope's detectors (image sensors) can introduce biases in astronomical observables such as photometry and astrometry that propagate into shear measurement biases. These type of errors have been extensively studied in the case of thick, fully-depleted, high-resistivity Charge Coupled-Devices (CCDs), which are the detectors of choice for many current and planned surveys such as DES, HSC, and LSST \citep{stubbs14,plazas14,gruen15}. It is of great importance to qualitatively quantify the impact of these sensor effects on the inference of cosmological parameter, in particular through WL \citep{jarvis14,mandelbaum14b,meyers14}. Future missions such as the James Webb Space Telescope and \wfa\ will utilize a new family of near-infrared detectors that are subject as well to effects such as non-linearity, reciprocity failure \citep{bohlin05,biesiadzinski11}, interpixel capacitance (IPC) \citep{mccullough08,kannawadi15}, and persistence  \citet{smith08}, and that can potentially imprint biases on weak lensing shape measurements if not taken into account.

@@

In Section \S2 we summarize the main characteristics of the NIR detectors that will be used in \wfa\, and describe NL. In Section \S3 we describe the simulations we create to study NL for \wfa\ PSF profiles. Section \S4 presents our main results on fractional errors in size and absolute errors in ellipticity caused by NL, as function of relevant parameters such as mean non-linearity amplitude and PSF magnitude. We also study the effect of the spatial variability of $\beta$ along the pixel array. We conclude in Section \S5 with a discussion of our results and how they can be used in the derivation of NIR detector specifications to satisfy WL accuracy requirements.

@@

The last two types of non-linearity depend on fluence (total flux per pixel, or integrated signal, as opposed to RF, which is flux dependent), and can be analyzed together in a singe transfer function typically called ``nonlinearity" (NL). We study the impacts of NL (more relevant at high signals) on PSF measurements in this paper, while we leave investigations on the consequences of RF (relevant at lower signals) on WL measurements for future work.

To obtain a functional model of NL as a function of signal, we use laboratory measurements\footnote{Performed at Caltech by R. Smith and collaborators} of H2RG 1.7$\mu$m cutoff detectors, which have the same basic design of the H4RG that will be used in the WFI but with 18 $\mu$m pixels. A constant flux source is illuminated on the detector, and the NL measurements are done by non-destructive sample-up-the-ramp (SUTR) readout at multiple times. The value of the first frame is subtracted, and then the \emph{mean} signal is fitted to a polynomial. These measurements show that the voltage relation for a measured signal $S$ is well fit by a quadratic function in the mean signal $\langle Q \rangle$ of the form:
\begin{align}
S(\langle Q \rangle)=\langle Q \rangle-\beta \langle Q \rangle^2 \ \ (e^{-})
\label{NL}
\end{align}
To determine the scale of spatial variation in NL among the individual pixels, high S/N co-added flats were taken at different exposure times and constant flux, and their ratios taken (after subtraction of a mean dark flat for each frame). The sequence of means of the ratio images followed the quadratic function of Eq. \ref{NL}, and the standard variation includes shot noise and deviations of the individual NL curves from the mean NL. After subtracting in quadrature the contribution from shot noise, a remaining floor in the variation of about $12\%$ r.m.s. can be attributed to the variation of the NL coefficient $\beta$.  Thus, we assume that each individual pixel satisfies a NL function of the same form as Eq. \ref{NL}, and that the spatial variation on NL is such as the non-linearity coefficient $\beta$ in each pixel can be drawn from a Normal distribution of the form $\mathcal{N} \sim (\beta_0, 0.12\beta_0)$, where the nominal mean value $\beta_0$ is measured to be $3.566\times10^{-7}/e^{-}$. This mean nominal value implies an attenuation of the signal of about $4\%$ for a pixel full well depth in the WFI detectors of $1.1 \times 10^5$ electrons (Eq. \ref{NL}).

We assume that galaxies will have about two orders of magnitude less total electrons than bright stars, and therefore for this quadratic model, star shapes are distorted by NL and galaxies are (approximately) not, which would result in incorrect PSF correction if not accurately calibrated. We apply this mapping to simulated \wfa\ PSF profiles and quantify the impact on PSF properties such as size and shape.

%We have verified that the results using the mean NL coefficient for all pixels do not differ significatively from those using the distribution above for each pixel (see Section and Table 2 below).

% DC offsets which are intrinsic to the readout circuit and which vary from pixel to pixel

@@

\citet{kannawadi15} have developed within \gs\ (v1.3) a \wfa\ module called ``{\tt{galsim.wfirst}}", which allows the simulation of a PSF profile according to the optical design characteristics of the \wfa\ WFI \citep{pasquale14})\footnote{\citet{pasquale14} discuss the so-called ``Cycle 4" optical design, whereas the \gs\ \wfa\ module -used in this work- uses files corresponding to ``Cycle 5"}) through the calling of {\tt{galsim.wfirst.getPSF}} routine. This routine returns a {\tt{python}} dictionary of {\tt{galsim.ChromaticOpticalPSF}} objects indexed by each one of the 18 H4RG detectors of the FPA. It uses the optical configuration of the pupil plane to simulate PSF images in any \wfa\ WFI bandpass filter, with expected optical aberrations approximated as a linear combination of Zernike polynomials (up to Noll order equal to $11$, \citet{noll67}). For this work, we have created simulations in four bands of the HLS (see Table 1).  A central circular obscuration ($30 \%$) and six support struts are included as well. The pupil plane configurations and Zernike models are publicly available.\footnote{\url{http://wfirst.gsfc.nasa.gov/science/sdt_public/wps/references/instrument/}}

@@

To overcome this problem in real data, multiple dithered exposures are taken, and then put together by means of an image combination algorithm \citep{lauer99b,fruchter02,bertin06,rowe11} in order to produce an oversampled image that satisfies the Nyquist-Shannon criterium. To study NL with simulations, however, we do not make use of such external software\textemdash which can be computationally expensive\textemdash to produce an image at higher resolution. Instead, we have used an approximation where we draw \gs objects at a high resolution through the method {\tt{galsim.GSObject.drawImage}}\footnote{The keyword {\tt{method}} should be set to {\tt{`no\char`_pixel'}} when calling {\tt{galsim.GSObject.drawImage}}, since by default it convolves its argument profile with a boxcar of length {\tt{pixel\char`_scale}}. This extra convolution must be turned off because the effective PSF profile we create already includes this pixel response.}, setting the parameter {\tt{scale}} to $p/N$, where $N\in \mathbb{Z}^{+}$ and $p$ is the native pixel scale. We apply the effect of NL to the convolved PSF profile, including the pixel response at its native scale, and then render it with a resolution $p/N$. 
Defining $Q\equiv1/p\times u_{\text{max}}$ as the sampling factor ($Q<2$, $Q=2$, and $Q\geq2$ represent under-, critically, and over-sampled images, respectively), we see that in order to produce an over-sampled image ($Q\geq2$), the Nyquist-Shannon criterium implies that $N$ must be given by (see \emph{e.g.}, \citet{marks09,shapiro13})
\begin{align}
N=\frac{2p}{\lambda_{min} F}
\label{nimages}
\end{align}
where $p$ is the pixel size, $\lambda_{min}$ is the shortest wavelength in a given filter, and $F$ is the the f-number of the telescope. In the case of the \wfa\ telescope, $p=10\ \mu$m and $F=7.8$, resulting in $N\geq3$ ($N\geq2$) for the J129 (H158) band. However, we have conservatively chosen a larger $N$ for our simulations to reduce discretization errors. We have verified the convergence of our results for $N\geq6$.  
%However, we oversample the images at  the error due to discretizing, and to reduce the variance due to any sub-pixel offsets that PSFs may have. We have set $N$ equal to $6$ for our simulations.

@@

The PSF profiles are drawn into square postage stamps of size 1.5k pixels (k=1024), large enough to ensure that most of the flux applied to the original profile object is conserved when drawing the image. %In addition, this avoid biases in PSF determination arising from object selection and deblending. 
Each profile object was assigned a total flux of 
\begin{align}
f=k(\lambda)\times2.521^{(20-m)} \ e^{-}, 
\label{flux}
\end{align}
which is the number of source counts per exposure and where $m$ represents the AB magnitude of the object. $k(\lambda)$ e$^{-}$ is a baseline flux at AB magnitude $m=20$ determined by using the \wfa\ Exposure Time Calculator\footnote{\url{https://wfirst.ipac.caltech.edu/sims/tools/wfDepc/wfDepc.html}} \citep{hirata12} in weak lensing mode (ETC-WL). Notice that in our simulations we have neglected the main sources of noise that would affect the HLS\textemdash zodiacal background, thermal emission, and read noise, which would make all images slightly more nonlinear. Calculations performed with the ETC-WL by \citet{spergel15} in the F184 band (a conservative case) show that the background contribution due to these backgrounds sources would be of the order of 130 $e^-$ per pixel for a $174 s$ exposure (\emph{c.f.,} Appendix), negligible compared with the values used in our simulations (Table 1).

@@

The basic process is summarized by the following steps:  
\begin{itemize}
\item[1.] Create a \wfa\ PSF surface brightness profile with a given flux as prescribed by Eq. \ref{flux}. 
\item[2.] Convolve the PSF profile with a squared pixel response with the size of the native plate scale of the \wfa\ FPA ($p=0.11$ arcseconds per pixel) to produce an effective PSF. 
\item[3.] Draw the effective PSF profile in a noiseless postage stamp of size $1.5k$ by $1.5k$ pixels ($k=1024$) pixels at a higher resolution of of $p/N$, with $N=6$, and multiply the resulting image by $N^2$. In this step, NL is not yet applied, but it will be done so in a later step, so the flux still needs to be adjusted. 
\item[4.] Use the adaptive moments algorithm to measure the shape $e=(e_{1,0},e_{2,})$ and size $R_0$ of the profile to have as baseline reference.
\item[5.] Create another image of the effective PSF at a higher resolution and with the flux adjusted as in 3. To apply NL, draw a $\beta$ from the distribution $\mathcal{N} \sim (\beta_0, 0.12\beta_0)$ for each pixel in the high-resolution image $I$, and apply the voltage non-linearity to the postage stamps according to the transformation $I \mapsto I - \beta I^2$ (\emph{c.f.} Eq. \ref{NL}.)
\item[6.] Measure the shape and size of the object with the sensor effect applied, and calculate the quantities $\Delta e_1$, $\Delta e_2$, and $\frac{\Delta R}{R}$, as defined in Eqs. \ref{delta_e} and \ref{delta_r}. 
\item[7.] Repeat steps 5 and 6 for $M$ realizations of the $\beta$ distribution, and calculate the mean value of Eqs. \ref{delta_e} and \ref{delta_r} over all $M$ realizations. The error bars will be given by the standard error of the mean. In our simulations we use $M=100$, although we have found little impact on the metrics used due to the spatial variation of $\beta$ (see Section \S\ \ref{results} and Fig. \ref{diff})
\item [8.] Repeat  steps 1 to 7 for different AB magnitudes (fluxes) at fixed mean $\beta$ and for different NL parameters at a fixed magnitude. 
\end{itemize}
\section{Results}
\label{results}
Fig. \ref{beta} shows the fractional change in PSF size and the absolute error in PSF ellipticity as a function of the mean nonlinearity parameter $\beta$, for different bandpass filters at fixed AB magnitude of 20, consistent with the magnitude of brightest stars that will be usable for the HLS. The effect depends on flux, and hence its amplitude is the largest in the J129 bandpass filter (\emph{c.f.}, Table 1). 
\begin{figure}[!h]
\centering
\resizebox{\hsize}{!}{\includegraphics[page=1]{plots/delta_e_delta_r_r_M_100-22-1-16.pdf}}
\caption{Fractional error in PSF size (upper panel) and absolute error in PSF ellipticity components (lower panels) as a function of the mean nonlinearity parameter $\beta$ for the \wfa\ PSF, in four the four HSL filters (J129, Y106, H158, and F184), and an AB magnitude of 20 (similar plots were found for other values of magnitude). In each plot, the nominal value for the nonlinearity parameter as given by laboratory measurements, $\beta_0$, is located at the third point from the origin. Each point is the mean over $M=100$ realizations of the parameter $\beta$ per pixel, and the associated error bars (too small to be seen in the cases of $\Delta R/R$ and $\Delta e_2$) represent the standard error of the mean.}
\label{beta}
\end{figure}
In this band, the mean nominal value of $\beta_0=3.566\times10^{-7}/e^{-}$ induces errors in the size and ellipticity of about $5\times10^{-3}$ and $8\times10^{-4}$ respectively, comparable or even larger than the required values of $10^{-3}$ and $4.5\times10^{-4}$ on the knowledge of the size and ellipticity of the PSF in order not to bias cosmological parameter inferences from WL experiments (Section \S1). As the $\beta$ parameter is increased, the amplitude of the errors increases approximately in a linear manner within the domain of $\beta$ values considered.

%It is possible to obtain a more general relationship between $\Delta R/R$ (or $\Delta e$), $\beta$, and object flux for each band by Taylor expanding to first order around any given value in $\beta$ and plotting the slope as a function of magnitude. 
Since $\Delta R/R$ and $\Delta e$ are approximately linear in $\beta$, we can condense this information by simply plotting the slope for various filters and star magnitudes.This is shown in Fig. \ref{magnitude}, which shows $\Delta R/R/\beta$ and $\Delta e/\beta$ (the slopes in Fig. \ref{beta}) vs $m$ for each of the four filters of the HLS. From Fig. \ref{magnitude}, it is possible to estimate the precision to which $\beta$ would have to be calibrated in order to limit the relative size and ellipticity bias of a star with a given magnitude. In particular, letting $(\beta - \beta_0)/\beta_0 \equiv \Delta \beta / \beta_0$ represent the fractional error in the measurement of a given value of $\beta_0$, we have: 
\begin{align}
\frac{\Delta R/R}{\Delta \beta} = c \ \ \ \  \Rightarrow \ \ \ \ \frac{\Delta R/R}{\Delta \beta / \beta_0} = c \beta_0  \ \ \   \Rightarrow \ \ \
\frac{\Delta \beta}{\beta_0} = \frac{\Delta R/R}{c \beta_0}
\label{calib}
\end{align}
In Eq.\ref{calib}, $c$ represents the ordinate value in Fig. \ref{magnitude} for a given magnitude, and we have replaced $\Delta R/R/\beta$ by $\Delta R/R/ \Delta \beta$ since the linearity in the bias in $\Delta R/R$ and $\Delta e$ vs $\beta$ for all magnitudes makes the choice of the expansion point of the approximation by Taylor expansion unimportant (\emph{i.e.}, it does not matter if the expansion is around $\beta=0$ or $\beta=\beta_0$). An analogous equation to Eq. \ref{calib} can be written for the error in the ellipticity if $\Delta R/R$ is replaced by $\Delta e$.

@@

We also studied the impact on $\Delta e$ and $\Delta R/R$ due to the dispersion in the $\beta$ parameter. As mentioned before, each pixel can have a different NL coefficient and biases in the measurement of PSF properties could be introduced if using a mean response curve to calibrate NL instead of a single curve per pixel. We calculated the difference between the values of $\Delta e$ and $\Delta R/R$ obtained when assuming that each pixel has a different NL coefficient drawn from the Normal distribution $\mathcal{N} \sim (\beta, 0.12\beta)$ (as has been assumed so far in our simulations), and when assuming that each pixel has a fixed coefficient given by the mean value $\beta$:
\begin{align}
d_{e_1} = \frac{\sum_{j=1}^{M=100} (\Delta e_{1,j}^{\text{dist}}  - \Delta e_1^{\text{fix}}) } {M}
\label{diference}
\end{align}
Analogous relations can be written for $\Delta e_2$ and $\Delta R/R$ as well (\emph{i.e.}, $d_{e_2}$, and $d_{\Delta R/R}$). Fig. \ref{diff} shows the average value of these differences over $M=100$ realizations for the nominal $\beta_0$, their standard deviation, and the standard error of each mean for all the four bands. We found values consistent with zero, indicating that for these simulations the impact of the individual $\beta$ variation is small.
